The Effects of Stellar Binarity on Transit Survey Occurrence Rates

### 2017-10-19 memos/toy_analytic_surveys_171010.tex
moving things around

However, the distance out to which double stars are {\it selected} is 
different from the distance $d_{{\rm max},d}^{\rm p}$ out to which planets can 
be {\it detected} (around the primary of a double star system).
For the binary twin population, all planet and stellar radii are identical, so 
${\rm S/N} \propto \mathcal{D}, and
L^{1/2} d^{-1}$,
\begin{equation}
d_{{\rm max},d}^{\rm p} = (1 + \gamma_R)^{-1/2} d_{{\rm max},s} = 
(1 + \gamma_R)^{-1} d_{{\rm max},d}.
\end{equation}
For $\gamma_R = 1$, this means only 1 in 8 apparently-searchable stars which 
are in fact binary systems can yield detectable planets (the ratio of 
volume in which planets can be detected to the actual selected volume).

@@

The true occurrence rate is the average number of planets of the desired type 
per star of the desired type.
The number of planets of the desired type is
\begin{equation}
N_{\rm planets} = \Gamma_{t,s}N_s + \Gamma_{t,d}N_d + 
\Gamma_{t,d}w_{d2}f_{{\rm desired}}N_d,
\end{equation}
where as before $N_s$ and $N_d$ are the number of single and double systems, 
and the fraction $f_{{\rm desired}}$ is defined so that $f_{{\rm desired}} 
N_d$ is the number of secondaries that are of the desired type, and as before 
$\Gamma_{t,d}w_{d2}$ is the average number of planets each of these desired 
stars hosts.
Explicitly,
\begin{equation}
f_{\rm desired} = \frac{\int_{M_{\rm min}}^{M_{\rm max}} {\rm prob}_{\rm 
        ml}(q)\,{\rm d}q }
{\int_{0.1M_1}^{M_1} {\rm prob}_{\rm 
        ml}(q)\,{\rm d}q}.
\end{equation}
For instance, assuming a primary mass of $M_1 = M_\odot$, and defining the 
``desired type'' of stars being to be $0.7<M_\star/M_\odot<1.3$, we find 
$f_{\rm desired}\approx0.475$.

>>>>

However, the distance out to which double stars are {\it selected} is 
different from the distance $d_{{\rm max},d}^{\rm p}$ out to which planets can 
be {\it detected} (around the primary of a double star system).
For the binary twin population, all planet and stellar radii are identical, so 
${\rm S/N} \propto \mathcal{D} L^{1/2} d^{-1}$, and
\begin{equation}
d_{{\rm max},d}^{\rm p} = (1 + \gamma_R)^{-1/2} d_{{\rm max},s} = 
(1 + \gamma_R)^{-1} d_{{\rm max},d}.
\end{equation}
For $\gamma_R = 1$, this means only 1 in 8 apparently-searchable stars which 
are in fact binary systems can yield detectable planets (the ratio of 
volume in which planets can be detected to the actual selected volume).

@@

The true occurrence rate is the average number of planets of the desired type 
per star of the desired type.
The number of planets of the desired type is
\begin{equation}
N_{\rm planets} = \Gamma_{t,s}N_s + \Gamma_{t,d}N_d + 
\Gamma_{t,d}w_{d2}f_{{\rm desired}}N_d,
\end{equation}
where as before $N_s$ and $N_d$ are the number of single and double systems, 
and the fraction $f_{{\rm desired}}$ is defined so that $f_{{\rm desired}} 
N_d$ is the number of secondaries that are of the desired type, and as before 
$\Gamma_{t,d}w_{d2}$ is the average number of planets each of these desired 
stars hosts.
Explicitly,
\begin{equation}
f_{\rm desired} = \frac{\int_{q_{\rm min}}^{q_{\rm max}} {\rm prob}_{\rm 
        ml}(q)\,{\rm d}q }
{\int_{0.1}^{1} {\rm prob}_{\rm 
        ml}(q)\,{\rm d}q}.
\end{equation}
For instance, assuming a primary mass of $M_1 = M_\odot$, and defining the 
``desired type'' of stars being to be $0.7<M_\star/M_\odot<1.3$, we find 
$f_{\rm desired}\approx0.475$.
